---
title: "Distance"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{distance}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, include = FALSE, setup}
library(disgraph)
```

## Graph distance methods to compare two networks.

The basic usage of a distance algorithm is as follows:


```{r, eval = FALSE}
library(disgraph)

graph <- matrix(
  cbind(
    c(0.0, 1.0, 0.0, 0.0),
    c(0.0, 0.0, 1.0, 0.0),
    c(0.0, 0.0, 0.0, 1.0),
    c(0.0, 0.0, 0.0, 0.0)
  ),
  nrow = 4
)

dist <- dist_frobenius(graph, graph)
```

Here, graph is a matrix but the api also works with igraph objects. The results are either a structure or numeric representing the distance value or computed side effects.

## Available distances

All of the following algorithms follow the same previous usage as above.

| function 	| algorithm  	|
|------	|---	|
| dist_frobenius | Frobenius Norm Distance|
| dist_hamming_ipsen_mikhailov | Hamming Ipsen Mikhailov Distance |
| dist_ipsen_mikhailov | Ipsen Mikhailov Distance |
| dist_laplacian_spectral | Laplacian Spectral Distance |
| dist_polynomial_dissimilarity | Polynomial Dissimilarity Distance |
